---
title: "Siegel, J., Arenson, M., Mikytuck, A., & Woolard, J. (2021). Engaging public policy with psychological science. Translational Issues in Psychological Science, 7(1), 1–8. https://doi.org/10.1037/tps0000284"
date: "Last update at: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: readable
    smooth_scroll: yes
    css: ../style.css

---

```{r echo=FALSE}
source("/Users/yuchenwei/Desktop/Academy/R Markdown settings/functions.R")
library(tidyverse)
```
```{css}
.btn-group{
  display:none;
}
.title {
  color: white;
}
h1{
  color: lightgreen;
  font-family: Georgia;
}
h2, h3, h4{
  color: pink;
  font-family: Georgia;
}
```


# Back to index 

[Back to index](../Final project.nb.html)

# Abstract / Key ideas 

Policymaking is a complex system with multiple individual and organizational stakeholders 

Policymaking process is more than a simple linear or even circular process and instead is a dynamic recursive process 

We must know what is considered research and how research might or might not be used in that complex system process 

Mention NU's program on P3, left col

# Lit rev 

Psychological scientists often have a litmied understanding of appropriate ways to engage with and transalte their science to public policy arenas 

# Public policy as a complex system 

- not just legistors, but including advocates, interest groups, media, and individuals ---> are part of the larger policy ecosystem and can influence agenda and advocate for change 

- policy made ≠ implemented 

## Using researchi in the public policy process 

`r colored("Research is more often used before the issue becomes an issue ---> before ideologies and positions have solidified", "gold")` <br> ---> `r colored("preemptive and future-oriented approach", "coral")`

Psychological org with a clear policy focus: 

  - Society for the Psychological Study of Social Issues 
  - Society for Child and Family Policy and Practice 
  - Society fo Research in Child Development 
  - Siceity for Community Research and Action 

## The mutual influence of research and policy 

  - acknowlege positionality and social location 
  - knowledge is *cocreated* between researchers and the researched 
  

<hr>

# Other relevent lit

Tropp, 2018 

John, 2017 ***

-----
[Back to index](../Policy-Index.nb.html)

```{r echo=FALSE}
file.copy("Final project empty.Rmd", "Ford 2023")
file.rename("./Ford 2023/Final project empty.Rmd", "./Ford 2023/Ford 2023.Rmd")
file.edit("./Ford 2023/Ford 2023.Rmd")
```

`r colored("", "gold")`

















  

