---
title: "Nosek, B. A., Hardwicke, T. E., Moshontz, H., Allard, A., Corker, K. S., Dreber, A., Fidler, F., Hilgard, J., Kline Struhl, M., & Nuijten, M. B. (2022)."
subtitle: "Replicability, robustness, and reproducibility in psychological science. Annual Review of Psychology, 73, 719–748."
date: "Last update at: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: readable
    smooth_scroll: yes
    css: ../style.css

---

```{r echo=FALSE}
library(tidyverse)
source("../functions.R")
```

```{css}
.btn-group{
  display:none;
}
```

# Back to index 

[Back to index](../index.nb.html)

# Abstract / Key Points

Reproducibility: 

  - process: data, code, info needed to create the code or necessary software of tools  
  - outcome: results 

Robustness: results do not vary with the decisisions to include/exclude certain covariates 

  - A `r colored("fragile", "gold", bold = T)` finding is not necessarily wrong 
  - A fragile finding can amplify concerns about p-hacking and overfitting that reduce credibility 

Machine learning can have the statistics and the narrative text as the input and output whether the study would replicate (p.729)


-----
[Back to index](../index.nb.html)


```{r echo=FALSE, results='hide'}
empty_file = "Empty.Rmd"
new_article = "Nosek_etal_2013"
new_new_article_md = stringr::str_c(new_article,".Rmd")
new_folder_path = stringr::str_c("./", new_article)

old_path = stringr::str_c("./", new_article, "/", empty_file)
new_path = stringr::str_c("./", new_article, "/", new_new_article_md)

dir.create(new_article) #create a new folder
file.copy(empty_file, new_article) #move the current file to that folder 
file.rename(old_path, new_path) #rename the current file 
file.edit(new_path)
```

`r colored("", "gold", bold = T)`


















  

